Using numerical modelling to investigate temperature and wave exposure as drivers of macroalgal characteristics

### 2019-08-27 morphology_paper.Rmd
word output updated. general house cleaning.

```{r schematic, echo=FALSE, fig.cap='Schematic of *L. pallida* and *E. maxima* morphology.', fig.height=6, fig.width=6}

@@

```{r rda eck plots, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}
ggarrange(lam_rda, rda_eck_deep, rda_eck_shallow, common.legend = TRUE, legend = "bottom", labels = "AUTO",ncol = 2, nrow = 2)
```

>>>>

```{r schematic, echo=FALSE, fig.cap='Schematic of *L. pallida* and *E. maxima* morphology [@Dyer2018-rv].', fig.height=6, fig.width=6}

@@

```{r rda eck plots, echo=FALSE, fig.height=7, fig.width=8, message=FALSE, warning=FALSE}
ggarrange(lam_rda, rda_eck_deep, rda_eck_shallow, common.legend = TRUE, legend = "bottom", labels = "AUTO",ncol = 2, nrow = 2)
```
